Object Categorization based on RGBD data

### 2013-10-20 Disseration/experiments.tex
desc_b3do fig

>>>>

	\begin{figure}[!ht]
	\centering	
	\includegraphics[width=.75\textwidth]{figs/desc_b3do}
	\caption{Highest accuracy obtained with FPFH, PFH and PFHRGB descriptors on the B3DO dataset}
	\label{fig:desc_b3do}
	\end{figure}

	The figure \ref{fig:desc_b3do} shows highest accuracy obtained with the tested descriptors on the B3DO dataset. FPFH scored the best result, even tough it is an approximate and theoretically the least precise of all evaluated descriptors. On the other hand, the PFHRGB scored better than PFH. It does not surprise, since the colour information is believed to have discriminative value.
